---
title: "rcsi documentation"
author: "Jerry Magnin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Info

`rcsi` was written to provide a simple tool to read Campbelle Scientific (r) dataloggers output. It currently supports the following formats:

* TOA5 (ASCII table with 4-row header)
* TOACI1 (ASCII table with 2-row header)

It will provide, in further version, support for:

* TOB1 (binary table with ASCII header)

Automatic file format detection is also planned for a future revision.

# Usage

First, you need to import the package inside your workspace with `library(rcsi)`.
Once it's done, call the function you need, depending on the file type. In the following example, we will use the `TOA5TestSet.dat` TOA5 example file provided in the `test/testthat` directory.

```{r importData}
library(rcsi)
dat <- importTOA5data('../tests/testthat/TOA5TestSet.dat', RetOpt = 'all', time = 'POSIXct')
print(dat)
```

Now your data is imported, you can manipulate it as R objects. For this example, I imported both header & data in a list, so I have to specify the part of my object I want to manipulate.

```{r plotData}
plot(x = dat$data$TIMESTAMP, y = dat$data$PTemp, type="b")
```

You can also reshape your data & plot them with `ggplot2`
```{r ggplot2 usage}
library(reshape2)
library(ggplot2)

reshapedDat <- melt(data = dat$data[c('TIMESTAMP', 'RECORD', 'PTemp')], id.vars = c('TIMESTAMP', 'RECORD'))
print(reshapedDat)

plt <- ggplot(reshapedDat) + geom_line(aes(x=TIMESTAMP, y = value, colour = variable))
plt
```